### 2019-03-14 proposals/TESS_GI_cycle02/tessgi_gully_cycle2.tex
more and more prose and now more equations

\usepackage{caption}
\usepackage{subcaption}

@@

\subsection{Kepler and Tess perceive different starspot contrast}

@@

The spot contrast is wavelength dependent ($c_\lambda$), and can be thought of as possessing a spot temperature, $T_{spot}$, distinct from the ambient photosphere $T_{phot}$.

@@

The spot contrast ratio---evaluated at these two pairs of bandpasses---provides a unique solution to $T_{phot}(\mathrm{SpT},\;P_{\mathrm{rot}})$.  Operationally, integrating the specific intensity $I_\lambda(T_{phot})$ over the system throughputs produces the expected contrast ratios.  For now we assume $I_\lambda(T_{phot})$ can be approximated as a stellar photosphere, such as the \texttt{PHOENIX} model grid.

Rotationally-modulated lightcurves exhibit semi-sinusoidal undulations as starspots (or spot groups) enter and exit the projected stellar disk.  The most-spotted projected hemisphere is directed towards the observer at the moment of the lightcurve minimum, and the least-spotted projected hemisphere at lightcurve maximum.  The amplitude of the lightcurve therefore equals the difference in starspot coverage fractions between the most-and-least spotted projected hemispheres \emph{multiplied by the spot contrast}.

\subsection{Different amplitudes and periods for a large fraction of stars from TESS data}

Rapid rotators tend to exhibit larger amplitudes of lightcurve undulations than slower rotators.  The amplitude of the If starspots were completely non-emitting across all wavelengths, \kepler\ and \tess\ would measure the same

\subsection{Compute the typical ratio of Kepler/K2 amplitudes to TESS amplitudes at given SpT/rotation rate}
\subsection{Interpret the Tess/Kepler ratios as spot contrast differences}
\subsection{Get starspot temperature and coverage fraction for a subsample of these stars from spectroscopy}
\subsection{Compute the ratio of TESS amplitude to total spot coverage}
\subsection{Compute a regression of spot coverage to rotation rate and spectral subtype.}

@@

\subsection{Measuring periods and amplitudes, which has been demonstrated}
\subsection{There will be enough GKM stars}
\subsection{The TESS precision will be adequate}
\subsection{Experience with the spectral technique on young stars}
\subsection{Availability of archival spectroscopy}

>>>>

\usepackage{caption}
\usepackage{subcaption}
\usepackage{cancel}

@@

\subsection{Kepler and TESS perceive different starspot contrast}

@@

The spot contrast is wavelength dependent ($c_\lambda$), and can be thought of as possessing a characteristic spot temperature, $T_{spot}<T_{phot}$ that parameterizes the wavelength dependence of the contrasts.

@@

The spot contrast ratio---evaluated at these two pairs of bandpasses---provides a unique solution\footnote{Operationally, integrating the specific intensity $I_\lambda(T_{spot})$ over the system throughputs produces the expected contrast ratios.  For now we assume $I_\lambda(T_{spot})$ can be approximated as a cooler stellar photosphere, such as the \texttt{PHOENIX} model grid \citep{2013A&A...553A...6H}, an inexact but adequate assumption for the large bandpasses.} to $T_{spot}(\mathrm{SpT},\;P_{\mathrm{rot}})$.

\subsection{Spot-induced modulation amplitudes depend on contrast}
Rotationally-modulated lightcurves exhibit semi-sinusoidal undulations as starspots (or spot groups) enter and exit the projected stellar disk.  The most-spotted projected hemisphere is directed towards the observer at the moment of the lightcurve minimum, and the least-spotted projected hemisphere at lightcurve maximum.  The amplitude of the lightcurve therefore equals the difference in starspot coverage fractions $\Delta f_{spot}$ between the most-and-least spotted projected hemispheres \emph{weighted by the spot contrast}:

$$ A_\lambda = \Delta f_{spot} \cdot (1-c_\lambda)$$

Therefore the ratio of \tess\ to \kepler\ amplitudes yields a constraint independent of the actual spot coverage fraction:

$$ \frac{A_{TESS}}{A_{Kepler}} = \cancel{\frac{\Delta f_{spot}}{\Delta f_{spot}}} \cdot \frac{1-c_{TESS}}{1-c_{Kepler}} \label{eqn1}$$

\subsection{Measuring Kepler/K2 and TESS amplitudes: Statistical samples}
We see \ref{eqn1} above.
\subsection{Measuring Kepler/K2 and TESS amplitudes: The Kepler Prime Field}
\subsection{Interpret the Tess/Kepler ratios as spot contrast differences}
\subsection{Get starspot temperature and coverage fraction for a subsample of these stars from spectroscopy}
%\subsection{Compute the ratio of TESS amplitude to total spot coverage}
%\subsection{Compute a regression of spot coverage to rotation rate and spectral subtype.}

@@

\subsection{Measuring periods and amplitudes, which has been demonstrated}
\subsection{There will be enough GKM stars}
\subsection{The TESS precision will be adequate}
Rapid rotators tend to exhibit larger amplitudes of lightcurve undulations than slower rotators.
\subsection{Experience with the spectral technique on young stars}
\subsection{Availability of archival spectroscopy}
